Methods for Large Scale Learning to Rank

### 2014-09-19 report/Chapters/Results.tex
NDCG measurements + correcties implementatie

This chapter describes and discusses the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}. In addition, ranking accuracy results are included to validate the correctness of the Learning to Rank algorithm implementations.
\section{ListNet}
\subsection{Ranking accuracy}
\begin{table}[!h]
\centering
\begin{tabular}{p{6cm}p{1.6cm}p{1.4cm}r}\toprule
Dataset & RankLib & Cluster & Official evaluation \\
\midrule
OHSUMED (LETOR 3.0 version)     & 0.29          &   TODO & 0.3793 \\
MQ2008      					& 0.3865        &   TODO & 0.4689 \\
MQ2007      					& 0.2873        &   TODO & 0.4767 \\
MSLR-WEB10K 					& 0.1744     	&   TODO & - \\
MSLR-WEB30K 					& 0.1837     	&   TODO & - \\
\bottomrule
\end{tabular}
\caption{\acs{nDCG}@10 performance on the testing set on the first fold}
\label{tbl:accuracy_comparison}
\end{table}

>>>>

This chapter describes and discusses the results of the running time measurements of the cluster and baseline implementations as described in \ref{chap:implementation}. In addition, ranking accuracy results are included to validate the correctness of the Learning to Rank algorithm implementations.
\section{ListNet}
\subsection{Ranking accuracy}
\begin{table}[!h]
\centering
\begin{tabular}{p{6cm}p{1.6cm}p{1.4cm}r}\toprule
Dataset & RankLib & Cluster & Official evaluation \\
\midrule
OHSUMED (LETOR 3.0 version)     & 0.1144        &   0.3952 & 0.3793 \\
MQ2008      					& 0.3539        &   0.4969 & 0.4689 \\
MQ2007      					& 0.2581        &   0.5385 & 0.4767 \\
MSLR-WEB10K 					& 0.1744     	&   0.4023 & - \\
MSLR-WEB30K 					& 0.1837     	&   0.4020 & - \\
\bottomrule
\end{tabular}
\caption{\acs{nDCG}@10 performance on the testing set on the first fold}
\label{tbl:accuracy_comparison}
\end{table}
